Technical Report

### 2018-04-07 fully-abstract-comp/technical-report.tex
Propose LR for components, compatibility lemma for linking.

\begin{definition}[World specifies component]
  We define that a world $W$ specifies the presence of a component with global constants $\gc$
  \begin{equation*}
    \var{comp} = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  \end{equation*}
  (written as $W \vdash_\gc \var{comp}$)
  iff
  \begin{equation*}
    \vdash (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  \end{equation*}
  and there exist $r_1 \cdots r_n \in \dom(\pwheap)$ such that
  \begin{itemize}
  \item $\pwheap(r_i) = \codereg{\sigrets_i,\sigcloss_i,\code_i,\gc}$
  \item $\mscode = \biguplus_i \code_i$
  \item $\sigrets = \biguplus_i \sigrets_i$
  \item $\sigcloss = \biguplus_i \sigcloss_i$.
  \end{itemize}
\end{definition}

@@

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED?: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{TODO: Component logical relation. Rough sketch is in white-board-notes/leuven-23-3-2018-3.jpg (top left).}
\dominique{TODO: Compatibility lemma for linking: if $c_1$ and $c_1'$ are related and $c_2$ and $c_2'$, then so should be $c_1\bowtie c_2$ and $c_1' \bowtie c_2'$ (if defined).}
\lau{TODO: Version of FTLR for programs.}
\lau{TODO: Compatibility lemma for initial executable configuration construct, i.e. a lemma that says ``if two programs are related, then their initial executable configurations will be related''.}
\lau{TODO: A logical relation for executable configurations.}
\lau{TODO: contextual equivalence should be defined in terms of initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}

>>>>

\begin{definition}[World specifies component]
  We define that a world $W$ specifies the presence of a component with global constants $\gc$
  \begin{equation*}
    \var{comp}_0 = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  \end{equation*}
  (written as $W \vdash_\gc \var{comp}_0$)
  iff
  \begin{equation*}
    \vdash (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  \end{equation*}
  and there exist $r_1 \cdots r_n \in \dom(\pwheap)$ such that
  \begin{itemize}
  \item $\pwheap(r_i) = \codereg{\sigrets_i,\sigcloss_i,\code_i,\gc}$
  \item $\mscode = \biguplus_i \code_i$
  \item $\sigrets = \biguplus_i \sigrets_i$
  \item $\sigcloss = \biguplus_i \sigcloss_i$.
  \end{itemize}
\end{definition}

@@

\subsection{Related components}
\label{sec:related-components}

\begin{align*}
  \lrcomp(W) =
  \left\{\begin{multlined}
     \npair{\var{comp},\var{comp}} \;\mid \;\\
      \var{comp} = (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss) \tand \\
      W \vdash \var{comp} \tand\\
      \forall W' \ldotp \text{If } W \oplus W' \text{ is defined }\\
      \tand \overline{\npair{(c_{\mathrm{import}},c_{\mathrm{import}})}} \in \lrv(W')\\
      \text{then } \overline{\npair{(c_{\mathrm{export}},c_{\mathrm{export}})}} \in \lrv(W)
  \end{multlined}
    \right\} \cup
  \left\{\begin{multlined}
     \npair{(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d}),(\var{comp}_0,c_{\mathrm{main},c}, c_{\mathrm{main},d})} \;\mid \;\\
     \npair{(\var{comp}_0,\var{comp}_0)} \in \lrcomp(W) \tand
      W \vdash \var{comp} \tand\\
      \forall W' \ldotp \text{If } W \oplus W' \text{ is defined }\\
      \tand \overline{\npair{(c_{\mathrm{import}},c_{\mathrm{import}})}} \in \lrv(W')\\
      \text{then } \overline{\npair{(c_{\mathrm{export}},c_{\mathrm{export}})}} \in \lrv(W)
  \end{multlined}
    \right\} \cup
\end{align*}

\begin{lemma}
  If
  \begin{itemize}
  \item $\npair{(\var{comp}_1,\var{comp}_1)} \in \lrcomp(W_1)$
  \item $\npair{(\var{comp}_2,\var{comp}_2)} \in \lrcomp(W_2)$
  \end{itemize}
  then
  \begin{itemize}
  \item $\npair{(\var{comp}_1 \bowtie \var{comp}_2,\var{comp}_1\bowtie\var{comp}_2)} \in \lrcomp(W_1\oplus W_2)$.
  \end{itemize}
\end{lemma}

\section{Full Abstraction}
\lau{TODOs from last day in Leuven}
\lau{RESOLVED: components have optional main (pc/data pair)}
\lau{RESOLVED: linking component and context requires only one main (i.e., it is undefined if both or none of the two expose main.)}
\lau{RESOLVED?: Component logical relation. Rough sketch is in white-board-notes/leuven-23-3-2018-3.jpg (top left).}
\dominique{RESOLVED?: Compatibility lemma for linking: if $c_1$ and $c_1'$ are related and $c_2$ and $c_2'$, then so should be $c_1\bowtie c_2$ and $c_1' \bowtie c_2'$ (if defined).}
\lau{TODO: Version of FTLR for programs.}
\lau{TODO: Compatibility lemma for initial executable configuration construct, i.e. a lemma that says ``if two programs are related, then their initial executable configurations will be related''.}
\lau{TODO: A logical relation for executable configurations.}
\lau{TODO: contextual equivalence should be defined in terms of initial executable configuration.}
\lau{TODO: Did we agree that memory satisfaction should require $\stkb$ to be a free stack address (or at least not in the heap part)? I think we did.}
\begin{definition}
  \label{def:points-to-instr}
  A configuration $(\ms,\reg)$ {\sourcecolor or $\Phi = (\ms,\reg,\_,\_)$} is said to point to non-$\scall{}{}{}$ instruction $i$ in $A$ iff
  \[
    \reg(\pcreg) = ((\_,\_),\_,\eaddr,\aaddr) \tand \aaddr \in A
  \]
and
\[
  \decInstr{\ms(\aaddr)} = i
\]
\end{definition}
